A molecular dynamics study of the solvation of CO\textsubscript{2}, water, and some organic compounds in the ionic liquids [emim][B(CN)\textsubscript{4}] and [emim][NTf\textsubscript{2}]

### 2018-02-19 ionic_liquids.tex
inclusion of gitignore
add figures

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}
\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
\usepackage{scalerel}

\usepackage{adjustbox}   
\usepackage{threeparttable}
\usepackage{booktabs}
\usepackage{colortbl} 
\usepackage{xcolor}
\usepackage{float}
\usepackage{flafter}
\newcommand{\diff}[2]{\dfrac{\partial #1}{\partial #2}}

@@

We implemented in LAMMPS~\cite{Plimpton1995} the expanded ensemble methodology, as well as the codes regarding the \textit{soft-core} and DSF potential with linear coupling. All of this is available in repository https://github.com/atoms-ufrj/USER-ALCHEMICAL. The electrostatic interactions were calculated using the damped shifted force (DSF) method~\cite{Fennell2006} with $\alpha$ = 0.2 {\AA}$^{-1}$, with the exception of hexane, for which we considered full Coulombic interactions. For the systems modelled as rigid molecules, we employ the NPT method of Kamberaj~\textit{et al.}~\cite{Kamberaj_2005} using $\Delta t$ = 1 fs. For flexible systems, we employ the scheme due to Shinoda~\textit{et al}.~\cite{Shinoda2004}. PLAYMOL

@@

\subsection{Simulation strategies of ionic liquids}
\label{sec:prel_results}
In this section, we present results of preliminary simulations which to set the methodology employed in the simulations for free energy calculations. First, we considerd the ionic liquids as flexible ions.

@@

@@

>>>>

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}
\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
\usepackage{scalerel}
\usepackage{natbib}

\usepackage{adjustbox}   
\usepackage{threeparttable}
\usepackage{booktabs}
\usepackage{colortbl} 
\usepackage{xcolor}
\usepackage{float}
\usepackage{flafter}

\newcommand{\diff}[2]{\dfrac{\partial #1}{\partial #2}}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{graphicx,bm}
\usepackage[]{subfig}
\usepackage{epstopdf}

@@

We implemented in LAMMPS~\cite{Plimpton1995} the expanded ensemble methodology, as well as the codes regarding the \textit{soft-core} and DSF potential with linear coupling. All of this is available at https://github.com/atoms-ufrj/USER-ALCHEMICAL. The electrostatic interactions were calculated using the damped shifted force (DSF) method~\cite{Fennell2006} with $\alpha$ = 0.2 {\AA}$^{-1}$, with the exception of hexane, for which we considered full Coulombic interactions. For the systems modelled as rigid molecules, we employ the NPT method of Kamberaj~\textit{et al.}~\cite{Kamberaj_2005} using $\Delta t$ = 1 fs. For flexible systems, we employ the scheme due to Shinoda~\textit{et al}.~\cite{Shinoda2004}. Initial configurations were build using the PLAYMOL software available at https://github.com/atoms-ufrj/playmol.

@@

\subsection{Simulation strategies of ionic liquids}
\label{sec:prel_results}

In this section, we present results of preliminary simulations, which aimed at setting up a computational efficient protocol for the ionic liquids studied here.  As alternatives to standard approaches, in this work we assess the possibility of modeling the ions as rigid bodies and employing the DSF method for calculating the electrostatic interactions.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{ions_paper.pdf}
\caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
\label{fig:scheme}
\end{figure}

rigid-body configurations: We first carried out simulations of the isolated ion pairs in order to obtain the minimum energy configurations with respect to the corresponding (classical) model for each case.

@@

\begin{figure*}
\centering
\subfloat[text for the first subfigure\label{sfig:testa}]{%
  \includegraphics[width=.4\linewidth]{koller}%
}
\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=.4\linewidth]{batista}%
}

\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=.4\linewidth]{Liu}%
}
\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=.4\linewidth]{Weber}%
}
\caption{}
\label{}
\end{figure*}

\begin{figure}
\centering
\subfloat[text for the first subfigure\label{sfig:testa}]{%
  \includegraphics[width=\linewidth]{Ludwig}%
}

\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=\linewidth]{Ludwig_anion}%
}
\caption{}
\label{}
\end{figure}

@@

\begin{figure}
\centering
\subfloat[text for the first subfigure\label{sfig:testa}]{%
  \includegraphics[width=\linewidth]{kollerall.pdf}%
}

\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=\linewidth]{ludwigall.pdf}%
}
\caption{}
\label{}
\end{figure}
